

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
    \textbf{\Huge \scshape Balmukund Jha} \\ \vspace{1pt}
    \small +91 8294495929 $|$ \href{mailto:mukundjha204@gmail.com}{\underline{mukundjha204@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/mukundjha-mj/}{\underline{linkedin.com/in/mukundjha-mj/}} $|$
    \href{https://github.com/mukundjha-mj}{\underline{github.com/mukundjha-mj}}
\end{center}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Web Developer Intern}{June 2026 -- Present}
      {The Dark Store India Pvt. Ltd.}{Remote}
      \resumeItemListStart
        \resumeItem{Integrated third-party APIs and services to support core business and operational workflows, handling request/response logic and error handling.}
        \resumeItem{Built and maintained backend logic for e-commerce workflows, working with data layers to support dynamic storefront functionality.}
        \resumeItem{Collaborated with stakeholders to translate business requirements into scalable, maintainable web solutions.}
        \resumeItem{Optimized application performance through efficient data handling and reduced load times across key user flows.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
        {\textbf{CuraNet – Healthcare Records \& Consent Management System}}{\href{https://github.com/mukundjha-mj/curanet-backend}{GitHub} $|$ \href{http://curanet.in/}{Live}}\\[8pt]
        \emph{Node.js, Express.js, TypeScript, React.js, PostgreSQL, Prisma, JWT}
        \vspace{-0.5em}
        \resumeItemListStart
            \resumeItem{Built an EHR platform supporting 12 core workflows, 25+ REST endpoints, RBAC, and PostgreSQL-backed patient records with a 15+ table relational schema via Prisma ORM.}
            \resumeItem{Implemented consent-based access control allowing patients to grant, revoke, and time-limit provider access, with audit logging for all record access events.}
            \resumeItem{Developed a Universal Health ID system enabling seamless portability of medical records across multiple healthcare providers.}
    \resumeItemListEnd


    \resumeProjectHeading
      {\textbf{NetShield - Network Control and Website Blocking Tool}}{\href{https://github.com/mukundjha-mj/netshield}{GitHub}}\\[8pt]
      \emph{Node.js, Express.js, JavaScript, DNS, HTTP/HTTPS Proxy, CLI}
      \vspace{-0.5em}
      \resumeItemListStart
        \resumeItem{Developed a system-level network filtering tool to block distracting websites using domain- and keyword-based rules across HTTP/HTTPS traffic.}
        \resumeItem{Built a local proxy server and DNS filter in Node.js to inspect requests, enforce blocking rules, and return blocked responses in real time.}
        \resumeItem{Implemented a REST API and CLI to manage ban/unban workflows, with persistent rule storage and Windows proxy automation.}
      \resumeItemListEnd



    \resumeProjectHeading
      {\textbf{Microservices Uber Backend}}{\href{https://github.com/mukundjha-mj/Microservices-Uber-Backend}{GitHub}}\\[8pt]
      \emph{Node.js, Express.js, MongoDB, Microservices, JWT}
      \vspace{-0.5em}
      \resumeItemListStart
        \resumeItem{Built a scalable ride-hailing backend using Node.js, Express.js, and MongoDB with a microservices architecture.}
        \resumeItem{Implemented secure JWT-based authentication, trip booking workflows, and driver–passenger matching logic with real-time inter-service communication via message queues.}
        \resumeItem{Applied database indexing and query optimization, reducing API response time by 35\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
%-----------EDUCATION-----------
\section{Education} 
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology}{Vellore, TN}
      {Master of Computer Applications}{July 2024 -- April 2026}
    \resumeSubheading
      {Munger University}{Munger, BR}
      {Bachelor of Computer Applications}{May 2020 -- February 2024}
  \resumeSubHeadingListEnd





%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{\item{
\textbf{Languages}{: JavaScript, TypeScript, Python, Java, HTML, CSS} \\

\textbf{Frontend}{: React.js, Next.js, Tailwind CSS} \\

\textbf{Backend}{: Node.js, Express.js, REST APIs, Authentication (JWT, RBAC), Input Validation (Zod)} \\

\textbf{Databases \& ORM}{: PostgreSQL, MySQL, MongoDB, Prisma ORM} \\

\textbf{Caching \& Messaging}{: Redis, RabbitMQ} \\

\textbf{Architecture \& Concepts}{: Microservices Architecture, API Design, Database Design, DB Indexing, Query Optimization, Distributed Systems, OOP} \\

\textbf{Systems \& Networking}{: HTTP/HTTPS, DNS Fundamentals, Proxy-based Request Filtering, CLI Tools} \\

\textbf{DevOps \& Deployment}{: Docker, Linux} \\

\textbf{Tools \& Platforms}{: Git, GitHub}
}}
\end{itemize}





%-------------------------------------------
\end{document}
